---
title: "Coding Assignment 3"
author: "Team 3"
date: "Due: 2022-12-09 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#Put any packages you need here
library(readxl) # reading in excel file
library(car) # for vif function
library(plotly) # for interactive visualizations
library(gt) # better looking tables
library(gtsummary) #summary information
library(dplyr) #data manipulation package
library(corrplot) #correlation plot
knitr::opts_chunk$set(echo = TRUE)
```



A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
# Bring in the dataset here.
insurance <- read.csv("../Data/insurance_0026_Group3.csv")

#Display data
gt(head(insurance))
```

```{r}
bad_model <- lm(Charges ~., data = insurance)
summary(bad_model)
```
```{r}
tbl_regression(bad_model,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(bad_model)$adj.r.squared* 100,digits = 2),"%")))
```
```{r}
par(mfrow=c(2,2))
plot(bad_model)
```



## Question 1

Randomly select three observations from the sample and exclude from all modeling (i.e. n=47). Provide the summary statistics (min, max, std, mean, median) of the quantitative variables for the 47 observations.

```{r q1}
set.seed(123457)

index <- sample(seq_len(nrow(insurance)), size = 3)

train <- insurance[-index,]
test <- insurance[index,]

summary(train)
```
```{r}
train %>% 
  tbl_summary(statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median} ({p25}, {p75})",
                                                    "{min}, {max}"),
                              all_categorical() ~ "{n} / {N} ({p}%)"),
              type = all_continuous() ~ "continuous2"
  )
```

### Question 1 Observations
Based upon our observations of the data, we believe that age and smoker would have been indicative of higher rates. The mean is higher than the median, which means that the data is skewed right by over 3000. Range is significant, which indicates that there likely are outliers.


## Question 2

Provide the correlation between all quantitative variables

```{r}
#cor(insurance)
corrplot(cor(insurance),
type = "lower",
order = "hclust",
tl.col = "black",
tl.srt = 45,
addCoef.col = "black",
diag = FALSE)
```

```{r}
scatterplotMatrix(train[,1:3])
```
### Question 2 Analysis
No multicollinearity issues seem to be present.

## Question 3

Run a regression that includes all independent variables in the data table. Does the model above violate any of the Gauss-Markov assumptions? If so, what are they and what is the solution for correcting?

```{r}
model <- lm(Charges ~ ., data = insurance)
summary (model)
```
```{r}
par(mfrow=c(2,2))
plot(bad_model)
```
### Question 3 Analysis

We are going to try using logs and the quadratic regression value for age and BMI to transform the data. 

Due to the outliers of 9, 20, and 28, we have a nonlinear relationship, which means that the classical assumption has been violated. Since the normal Q-Q is not a 45 degree angle, it cannot be verified. Scale to location is not horizontal, and there are outliers, so we don't homoscedacticity. Residuals vs. leverage is not required to be included.

## Question 4

Implement the solutions from question 3, such as data transformation, along with any other changes you wish. Use the sample data and run a new regression. How have the fit measures changed? How have the signs and significance of the coefficients changed?

```{r}
#Log charges
par(mfrow=c(1,2)) 
hist(train$Charges)
train$lnCharges <- log(train$Charges)
hist(train$lnCharges)
```
```{r}
scatterplotMatrix(train[,c(10,2,3,4)])
```

```{r}
train$lnAge <- log(train$Age)
train$ageSquared <- train$Age^2
```

```{r}
model_1 <- lm(lnCharges ~., data = train[,c(10,11,3:5)] )
summary(model_1)
```
```{r}
tbl_regression(model_1,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(model_1)$adj.r.squared* 100,digits = 2),"%")))
```
```{r}
par(mfrow=c(2,2))
plot(model_1)
```

```{r}
model_2 <- lm(lnCharges ~., data = train[,c(11,3:5,10)]) 
summary(model_2)
```
```{r}
tbl_regression(model_2,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(model_2)$adj.r.squared* 100,digits = 2),"%")))
```
```{r}
par(mfrow=c(2,2))
plot(model_2)
```
### Question 4 Analysis
When you use the log of the charges, it makes a significant change to the distribution from skewed right to skewed normal. 

## Question 5

Use the 3 withheld observations and calculate the performance measures for your best two models. Which is the better model? (remember that "better" depends on whether your outlook is short or long run)

```{r q4}
test$lnCharges <- log(test$Charges)
test$lnAge <- log(test$Age)
test$AgeSquared <- test$Ageˆ2
```

```{r}
test$bad_model_pred <- predict(bad_model, newdata = test)
test$model_1_pred <- predict(model_1,newdata = test) %>% exp()
test$model_2_pred <- predict(model_2,newdata = test) %>% exp()
```
```{r}
test$error_bm <- test$bad_model_pred - test$Charges
test$error_1 <- test$model_1_pred - test$Charges
test$error_2 <- test$model_2_pred - test$Charges
```
```{r}
mean(test$error_bm)
```
```{r}
mean(test$error_1)
```
```{r}
mean(test$error_2)
```

```{r}
mae <- function(error_vector){
error_vector %>%
abs() %>%
mean()
}
```
```{r}
mae(test$error_bm)
```
```{r}
mae(test$error_1)
```
```{r}
mae(test$error_2)
```

```{r}
rmse <- function(error_vector){
   error_vector^2 %>% 
  mean() %>% 
  sqrt()

}

# Ins Model
rmse(test$error_bm)
# Model 1
rmse(test$error_1)

# Model 2
rmse(test$error_2)
```

```{r}
mape <- function(error_vector, actual_vector){
  (error_vector/actual_vector) %>% 
    abs() %>% 
    mean()
}

# Ins Model
mape(test$error_bm, test$Charges)
# Model 1
mape(test$error_1, test$Charges)

# Model 2
mape(test$error_2, test$Charges)
```

## Question 6

Provide interpretations of the coefficients, do the signs make sense? Perform marginal change analysis (thing 2) on the independent variables.

```{r}

```

## Question 7

An eager insurance representative comes back with five potential clients. Using the better of the two models selected above, provide the prediction intervals for the five potential clients using the information provided by the insurance rep.

| Customer | Age | BMI | Female | Children | Smoker | City           |
| -------- | --- | --- | ------ | -------- | ------ | -------------- | 
| 1        | 60  | 22  | 1      | 0        | 0      | Oviedo         |
| 2        | 40  | 30  | 0      | 1        | 0      | Sanford        |
| 3        | 25  | 25  | 0      | 0        | 1      | Winter Park    |
| 4        | 33  | 35  | 1      | 2        | 0      | Winter Springs |
| 5        | 45  | 27  | 1      | 3        | 0      | Oviedo         |


```{r}
#Customer 1
data.frame <- model_1
newPrediction <- data.frame(lnAge = 60, BMI = 22, Female = 1, Children = 0, Smoker = 0, WinterSprings = 0, WinterPark = 0, Oviedo = 1)
predict(model_1,
        newdata = newPrediction,
        interval = "confidence",
        level = .95)

#Customer 2
data.frame <- model_1
newPrediction <- data.frame(lnAge = 40, BMI = 30, Female = 0, Children = 1, Smoker = 0, WinterSprings = 0, WinterPark = 0, Oviedo = 0)
predict(model_1,
        newdata = newPrediction,
        interval = "confidence",
        level = .95)

#Customer 3
data.frame <- model_1
newPrediction <- data.frame(lnAge = 25, BMI = 25, Female = 0, Children = 0, Smoker = 0, WinterSprings = 0, WinterPark = 1, Oviedo = 0)
predict(model_1,
        newdata = newPrediction,
        interval = "confidence",
        level = .95)

#Customer 4
data.frame <- model_1
newPrediction <- data.frame(lnAge = 33, BMI = 35, Female = 1, Children = 2, Smoker = 0, WinterSprings = 1, WinterPark = 0, Oviedo = 0)
predict(model_1,
        newdata = newPrediction,
        interval = "confidence",
        level = .95)

#Customer 5
data.frame <- model_1
newPrediction <- data.frame(lnAge = 45, BMI = 27, Female = 1, Children = 3, Smoker = 0, WinterSprings = 0, WinterPark = 0, Oviedo = 1)
predict(model_1,
        newdata = newPrediction,
        interval = "confidence",
        level = .95)
```

## Question 8

The owner notices that some of the predictions are wider than others, explain why.

## Question 9 

Are there any prediction problems that occur with the five potential clients? If so, explain
